\mytitle{}

### 2018-01-10 paper/paper.tex
[Paper] Forgot something
[Paper] Slight nindent fix
[Paper] Fix on start template
[Paper] Updated thoughts non direction/approach

@@

\usepackage{hyperref}
\usepackage{url}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={Dynamically Annealed Reinforcement Learning for Intrusion Prevention},
	pdfauthor={Kyle A. Simpson}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

@@

\title{Dynamically Annealed Reinforcement Learning for Intrusion Prevention}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]},\\\emph{University of Glasgow, Glasgow, Scotland},\\
		\email{k.simpson.1@research.gla.ac.uk}}

@@

\begin{enumerate}
	\item Establish criteria used to inform system temp---what could make my system increase $\epsilon$ again late into training?
	\item What are my chosen features? Reward Function?
	\item Test against MARL and others---probably essential.
	\item Model at least three scenarios: standard (under attack), normality shifts, attack changes.
	\item \textsc{Ideally:} test adversarial work (what do such examples look like for my classifier, can an attacker actually operate on them?). How do results change with/without pretraining?
\end{enumerate}

>>>>

%% Fix indent in new section...
\newcommand{\subparagraph}{}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.5ex}{0.7ex}

@@

\newcommand{\mytitle}{%Dynamically Annealed Reinforcement Learning for Intrusion Prevention
Dynamic Exploration via the Wavelet Transform}

\usepackage{hyperref}
\usepackage{url}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={\mytitle{}},
	pdfauthor={Kyle A. Simpson}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

@@

\title{\mytitle{}}
\author{Kyle A. Simpson\thanks{This work was supported by the Engineering and Physical Sciences
		Research Council [grant number EP/M508056/1]},\\\emph{University of Glasgow, Glasgow, Scotland},\\
		\email{k.simpson.1@research.gla.ac.uk}}

@@

\begin{enumerate}
	\item Establish criteria used to inform system temp---what could make my system increase $\epsilon$ again late into training?
	\begin{enumerate}
		\item Current thoughts: Wavelet analysis of the reward signal.
		\item Intuition: multiscale representation of variation in reward.
		\item What do we see? Hopefully, state-to-state variation as well as longer-term characteristics.
		\item Expect that overall worsening on the coarsest scales should indicate pressing, global need for exploration  (i.e., non-stationarity, changing problem).
		\item We can perhaps derive a different uncertainty for each scale -- how do we choose? Combine answers, or (in turn) randomly select an $\epsilon$ from the derived set?
	\end{enumerate}
	\item What are my chosen features? Reward Function?
	\item What actions do I give the agents? Just more probabilistic packet dropping?
	\item Test against MARL and others---probably essential.
	\item Model at least three scenarios: standard (under attack), normality shifts, attack changes.
	\item \textsc{Ideally:} test adversarial work (what do such examples look like for my classifier, can an attacker actually operate on them?). How do results change with/without pretraining?
\end{enumerate}
